---
title: "Bank Customer Churn Analysis"
output: html_notebook
---

# Loading & Exploring the Dataset

```{r results='hide' }
library(readr)
library(tidyverse)

dset <- read_csv("~/Documents/workspace/Customer Churn/data/Churn_Modelling.csv")

```

```{r}
glimpse(dset)

```

We have 10,000 observation, each one with 14 feature/variable. The target variable is **Exited**. Let's check if there is missing data 

```{r}
sapply(dset, function(x) sum(is.na(x)))

# dset %>%
#   map_dfr(function(x) sum(is.na(x))) %>%
#   gather() %>%
#   ggplot(aes(reorder(key, -value), value)) +
#   geom_bar(stat = "identity", fill = "steelblue") +
#   #scale_y_log10(breaks = c(5, 50, 250, 500, 1000, 10000, 50000)) +
#   #geom_text(aes(label = value), vjust = 1.6, color = "white", size=3.5) +
#   theme_minimal() +
#   labs(x = "features", y = "Number of unique values") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

The happy case, we don't have any missing data!!

Look at the 14 variables, all of them are numeric. Let's check which ones are with categorical nature.
```{r}
(sapply(dset, n_distinct))

dset %>%
  map_dfr(n_distinct) %>%
  gather() %>%
  ggplot(aes(reorder(key, -value), value)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  #scale_y_log10(breaks = c(5, 50, 250, 500, 1000, 10000, 50000)) +
  #geom_text(aes(label = value), vjust = 1.6, color = "white", size=3.5) +
  theme_minimal() +
  labs(x = "features", y = "Number of unique values") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

* We can drop **RowNumber, CustomerID**, as they are just an index and user identifier.
* Geography, Gender, NumOfProducts, HasCrCard, IsActiveMember, and Existed are clear categorical variables.

```{r}
dset %>%
  select(-RowNumber, -CustomerId, -Surname) %>%
  mutate(Geography = as.factor(Geography),
         Gender = as.factor(Gender), 
         NumOfProducts = as.factor(NumOfProducts), 
         HasCrCard = as.factor(HasCrCard),
         IsActiveMember = as.factor(IsActiveMember), 
         Exited = as.factor(Exited)) -> dset
glimpse(dset)
```

# Exploratory Data Analysis 

## Exploring Numerical Variables Individually 
```{r}
old.par <- par(mfrow=c(2, 3))
hist(dset$CreditScore)
hist(dset$Age)
hist(dset$Tenure)
hist(dset$Balance)
hist(dset$EstimatedSalary)
par(old.par)
```

* Majority of customers age between 30s, and 40s
* Low balance is the common among available accounts
* Age and Tenure can be converted to categorical variable

```{r}
dset %>%
  mutate(Age = cut(Age, br = c(0,30,60,93),labels=c('young','adult','old'))) %>%
  mutate(Tenure = cut(Tenure, br= c(-1,3,7,10), labels=c('beginner','growing','mature'))) -> dset
```


## Explore Categorical Variables

```{r}
library(miscset)

ggplotGrid(ncol = 3,
lapply(c("Geography","Gender","NumOfProducts","HasCrCard","IsActiveMember", "Age", "Tenure", 
         "Exited"),
       function(col){
         ggplot(dset, aes_string(col, fill = "Exited")) + geom_bar()
       }))


```

* Femals are more likely to churn tham males. 
* Customers who have 3+ products are more likely to churn
* Adult members (30:60) are more likely to churn 
* Mature members (7+ Tenure) are less likely to churn
* Active members are less likely to churn than the inactive ones

# Prediction Models

## Prepare dataset 
```{r}
#install.packages("snakecase")
# library(snakecase)
# names(dset) <- to_snake_case(names(dset), sep_out = "_")
# 
# levels(dset$geography) <- to_snake_case(levels(dset$geography))
# levels(dset$gender) <- to_snake_case(levels(dset$gender))

#dset %>% mutate_if(is.factor, make.names) -> dset
levels(dset$NumOfProducts) <- c('one', 'two', 'three', 'four')
levels(dset$HasCrCard) <- c('No', 'Yes')
levels(dset$IsActiveMember) <- c('No', 'Yes')
levels(dset$Exited) <- c('No', 'Yes')

```


```{r}
# Create train/test indexes
library(caret)
set.seed(42)
myFolds <- createFolds(dset$Exited, k = 5)

# Create reusable trainControl object: myControl
myControl <- trainControl(
  summaryFunction = twoClassSummary,
  classProbs = TRUE, # IMPORTANT!
  verboseIter = TRUE,
  savePredictions = TRUE,
  index = myFolds
)

```

```{r results='hiden'}
#Glmnet Model
set.seed(42)
model_glmnet <- train(
 Exited ~ ., dset,
 metric = "ROC",
 method = "glmnet",
 tuneGrid = expand.grid(
 alpha = 0:1,
 lambda = 0:10/10
 ),
 trControl = myControl
)

plot(model_glmnet)
```

```{r results='hiden'}
# Random Forest
set.seed(42)
model_rf <- train(
 Exited ~ ., dset,
 metric = "ROC",
 method = "ranger",
 importance = 'impurity',
 trControl = myControl
)
plot(model_rf)
```

```{r results="hold"}
# GBM
set.seed(42)
model_gbm <- train(
 Exited ~ ., dset,
 metric = "ROC",
 method = "gbm",
 trControl = myControl
)
```

```{r}
#SVM
set.seed(42)
model_svm <- train(
 Exited ~ ., dset,
 metric = "ROC",
 method = "svmRadial",
 trControl = myControl
)
```

## Comparing different models
```{r}
# Make a list
model_list <- list(
 glmnet = model_glmnet,
 rf = model_rf,
 gbm = model_gbm,
 svm = model_svm
 )

# Collect resamples from the CV folds
resamps <- resamples(model_list)
resamps 

# Summarize the results
summary(resamps)

dotplot(resamps, metric = "ROC")

library(ranger)
plot(varImp(model_rf))

```

***